---
title: "MATH2270 Module 6"
author: "Alistair Grevis-James s3644119"
subtitle: Skill Builder
output:
  html_document:
    df_print: paged
---

#### Loading the Packages
```{r, message=FALSE, warning=FALSE}
library(ggplot2) #Required
library(dplyr) #Data wrangling
library(tidyr) #Data wrangling
library(rgeos) #Mapping
library(maptools) #Mapping
library(ggmap) #Mapping
library(broom) #Mapping
```

#### Data

The following exercises will be based on the lga_profiles_data_2011_pt1.csv dataset, introduced in Module 6.

```{r}
lga_profiles_data_2011_pt1 <- read.csv("lga_profiles_data_2011_pt1.csv")
```

#### Exercise 1

Create a choropleth map in Carto using the lga_profiles_data_2011_pt1 dataset covered in the Module 6 notes, but this time, look at a different variable that you find interesting. This will require you to sign-up for a Carto account if you haven’t already done so. Publish the map, add a title, and paste the link to the published plot in an RMarkdown report. Submit this link along with a solution to Exercise 2 below.

https://alistairgj.carto.com/builder/41a261c0-1601-456b-93f7-8ec569820676/embed

#### Exercise 2

Now recreate the choropleth map in Exercise 1 using ggplot2. Submit a knitted RMarkdown report to Canvas showing the link from Exercise 1 and the code and output from Exercise 2.

```{r, warning=FALSE}
vic.lga.shp <- readShapeSpatial("vmlite_lga_cm.shp")
lga_profiles_data_2011_pt1 <- read.csv("lga_profiles_data_2011_pt1.csv")
lga.shp.f <- tidy(vic.lga.shp, region = "lga_name")
lga.shp.f$lga_name <-lga.shp.f$id
merge.lga.profiles<-merge(lga.shp.f, lga_profiles_data_2011_pt1, 
                          by="lga_name", all.x=TRUE)
choro.data.frame<-merge.lga.profiles[order(merge.lga.profiles$order), ] 
p1 <- ggplot(data = choro.data.frame,
             aes(x = long, y = lat, group = group, 
                 fill = households_with_internet_connected)) +
  geom_polygon(color = "black", size = 0.25) + 
  coord_map() +
  scale_fill_distiller(name = "Fraction of Households",
                        guide = "legend",
                    palette = "YlGnBu", direction = 1) +
  theme_nothing(legend = TRUE) +
  labs(title="Fraction of Households with Internet Connected")
p1
```


```{r}
colnames(lga_profiles_data_2011_pt1)
```
